The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications

### 2017-04-20 paper.tex
Added more to time-bin section.

\subsubsection{Time-bins}
Time-bin qubits is quantum information that is encoded on the time-of-arrival of single photons. It was first conceived for a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}. If the photon passes through the shorter (longer) path, then it will arrive at the output port in an ``early" (``late") time bin. Thus, photon will exit the interferometer in a state that is a superposition of these two states. Owing to difficulties in implementing qubit operations in this basis, it was at that time mostly used for demonstrating quantum communication over long distance \cite{bib:Thew02,bib:Marcikic04}. With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operations, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}. At the same time, an ultrafast measurement technique for recovering time-bin qubits was also demonstrated \cite{bib:Donohue2013}.

>>>>

\subsubsection{Time-bins}
Time-bin qubits is quantum information that is encoded on the time-of-arrival of single photons. It was first conceived for a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}. If the photon passes through the shorter (longer) path, then it will arrive at the output port in an ``early" (``late") time bin labelled $\ket{e}$ ($\ket{\ell}$). Thus, photon will exit the interferometer in a state that is a superposition of these two states. Owing to difficulties in implementing qubit operations in this basis, it was at that time mostly used for demonstrating quantum communication over long distance \cite{bib:Thew02,bib:Marcikic04}. With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operations, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}. These gates form an universal set for quantum computing. At the same time, an ultrafast measurement technique for recovering time-bin qubits was also demonstrated \cite{bib:Donohue2013}.

In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin qubits have a polarization register which is used to toggle between the mode in which qubits are stored and transmitted, {\it i.e.} the ``register" mode, and the mode in which qubits are manipulated, {\it i.e.} the ``processing" mode using a polarization rotation. Other operations needed are a displacement operation moves a time-bin qubit in the processing polarization in time relative to other qubits, a partial polarization rotation between the register and processing polarizations to couple them, and a photon number measurement in a bin. The polarization rotation and polarization coupling operations were implemented using a fast integrated optical switch based on polarization-sensitive cross-phase modulation with a switching time of less than 10 ps. The displacement was implemented using a calcite crystal of a size that is of a path-length difference equal to an integer multiple of the time-bin separation. Using these operations and post-selection using a single-photon detectors, the authors were able to perform a heralded CPHASE gate \cite{bib:KLM01}.
